---
title: "Asistensi 2"
author: "Maharani Putri Efendi"
date: "2023-12-08"
output: html_document
---

## Import dataset.

## Exercise 2
Describe the distribution of score. Is the distribution skewed? What does that tell you about how students rate courses? Is this what you expected to see? Why, or why not?

1. Mengatur header 
```{r}
colnames(evals) <- evals[1,]
evals <- evals[-1, ]
```


2. Mengubah dataset menjadi numerik dan visualisasi data awal
```{r}
evals$score <- as.numeric(evals$score)
hist(evals$score)
```

## Exercise 3
Excluding score, select two other variables and describe their relationship using an appropriate visualization (scatterplot, side-by-side boxplots, or mosaic plot).

1. Melakuakn instalasi packages untuk plot

```{r}
install.packages("ggplot2")
library(ggplot2)
```

2. Mencari hubungan pada data categorical dengan visualisasi mosaicplot

```{r}
mosaicplot(table(evals$ethnicity, evals$language), shade =TRUE)
```


```{r}
mosaicplot(table(evals$rank, evals$cls_level), shade =TRUE)
```
warna biru maka nilai residualnya positif antara 2-4. Kalau putih nilai resiudalnya 0-2. 

residualnya semakin dikit maka korelasi variabelnya semakin besar. Semakin terang warnanya semakin tidak berkorelasi

##Exercise 4
Replot the scatterplot, but this time use the function jitter() on the y- or the x coordinate. (Use ?jitter to learn more.) What was misleading about the initial scatterplot?

1. Menampilakn visualisasi score dan average
```{r}
plot(evals$score ~ evals$bty_avg)
```
2. convert columns ke dalam numeric
```{r}
columns_to_convert <- c("age", "cls_per_eval", "cls_did_eval", "cls_student", "bty_f1lower", "bty_f1upper", "bty_f2upper", "bty_m1lower", "bty_m2upper", "bty_avg")
evals[columns_to_convert] <- lapply(evals[columns_to_convert], as.numeric)

# Plotting
plot(jitter(evals$bty_avg), jitter(evals$score))

```
3. melihat apakah variabel signifikan(???) 
```{r}
m_bty <- lm(score ~ bty_avg, data=evals)
```

4.Menampilkan korelasi antara bty_avg dan score
```{r}
cor(evals$bty_avg, evals$score)
```

5. Menampilkan plot untuk resiudal
```{r}
plot(m_bty$residuals ~ evals$score)
```
 titik2nya semakin banyak kumpul di 1 garis maka korelasinya semakin kecil.
 

##Exercise 5
Let’s see if the apparent trend in the plot is something more than natural variation. Fit a linear model called m_bty to predict average professor score by average beauty rating and add the line to your plot using abline(m_bty). Write out the equation for the linear model and interpret the slope. Is average beauty score a statistically significant predictor? Does it appear to be a practically significant predictor?

## Exercise 6


1. 
```{r}
plot(evals[, 13:19])
```

Plot diatas cenderung tinggi korelasinya. Karena bty ini mirip2 maka perlu didrop kolom dan hanya menggunakan bty avg

2. 
```{r}
m_bty_gen <- lm(score ~ bty_avg + gender, data = evals)
```

```{r}
summary(m_bty_gen)
```

```{r}
qqnorm(m_bty$residuals)
```


```{r}
qqline(m_bty$residuals)
```

```{r}
qqnorm(m_bty_gen$residuals)
```

```{r}
qqline(m_bty_gen$residuals)
```

jadi, penambhaan gender sebagai predictor/variabel independen akan menambah signifikasni linear modelnya


3. 
```{r}
m_bty_lan <- lm(score ~ bty_avg + language, data = evals)
```

```{r}
summary(m_bty_lan)
```
```{r}
m_bty_rank <- lm(score ~ bty_avg + rank, data = evals)
```

```{r}
summary(m_bty_rank)
```

```{r}
m_full <- lm(score ~ rank + ethnicity + gender + language + age + cls_perc_eval 
+ cls_students + cls_level + cls_profs + cls_credits + bty_avg 
+ pic_outfit + pic_color, data = evals) 
summary(m_full)
```



